\documentclass{article}
\usepackage {amsmath, amsfonts, amssymb, mathrsfs, amsthm, sectsty,hyphenat,enumitem,calc,url,color,array,tabu, stmaryrd, mathdots,comment}
%\usepackage{showlabels}
\usepackage{palatino}
\usepackage{comment}
\usepackage[all]{xy}
\usepackage[nottoc]{tocbibind}
\usepackage[toc,page]{appendix}
\usepackage{tocloft}

\renewcommand{\-}{\hyp{}}

\renewcommand\cftsecafterpnum{\vskip2pt}
\renewcommand\cftsubsecafterpnum{\vskip2pt}

\setlength{\parindent}{0pt} \setlength{\parskip}{10pt plus 2pt minus 1pt}
\topmargin=-0.5in \headheight=0in \headsep=0.25in \textheight=9.1in
\footskip=0.75in

%\input{"Users/kaletha/Work/TexMain/macros.tex"}
%\input{"C:/Users/Tasho/Documents/Dropbox/Work/TexMain/macros.tex"}
\input{macros.tex}



\sectionfont{\center\sc\normalsize}
\subsectionfont{\bf\normalsize}

\numberwithin{equation}{section}

\newcommand{\warn}[1]{{\leavevmode\color{red}[#1]}}

\begin{document}


We are grateful to the referee for their careful reading and their comments and suggestions. We have implemented most of their requests. For the remaining few, our answers are below.

(1) I don't understand this comment. If the question is about the uniqueness of Shelstad's first construction of the transfer factor, then the answer is that it is unique up to multiplication by -1, i.e. the pair of functions ${\Delta,-\Delta}$ is unique.

(2) No. $\bar z_\sigma$ denotes the value of the 1-cocycle $\bar z$ at $\sigma$, which is what is needed.


(6) I do not understand this comment. The claim is that there is a natural bijection between two sets -- the set of $\hat T$-conjugacy classes of $L$-homomorphisms $W_\R \to {^LT}_\pm$, and the set of genuine characters of $T(\R)_\pm$.

(23) The explanation is just about the notation. The proof of the formula is not given there. I have provided references for the proof.

(25) Provisos is correct.

(30) The constructions do not follow from [Kos78] or [Vog78]. They are just constructions that are used in various parts of the literature, and we are collecting and relating them to help readers navigate the literature.

(36) This is done 7 lines above the definition.

(41) I do not see the notation $G_x(\R)$ anywhere.

\end{document}