\documentclass{article}
\usepackage {amsmath, amsfonts, amssymb, mathrsfs, amsthm, sectsty,hyphenat,enumitem,calc,url,color,array,tabu, stmaryrd, mathdots,comment}
%\usepackage{showlabels}
\usepackage{palatino}
\usepackage{comment}
\usepackage[all]{xy}
\usepackage[nottoc]{tocbibind}
\usepackage[toc,page]{appendix}
\usepackage{tocloft}

\renewcommand{\-}{\hyp{}}

\renewcommand\cftsecafterpnum{\vskip2pt}
\renewcommand\cftsubsecafterpnum{\vskip2pt}

\setlength{\parindent}{0pt} \setlength{\parskip}{10pt plus 2pt minus 1pt}
\topmargin=-0.5in \headheight=0in \headsep=0.25in \textheight=9.1in
\footskip=0.75in

%\input{"Users/kaletha/Work/TexMain/macros.tex"}
%\input{"C:/Users/Tasho/Documents/Dropbox/Work/TexMain/macros.tex"}
\input{macros.tex}



\sectionfont{\center\sc\normalsize}
\subsectionfont{\bf\normalsize}

\numberwithin{equation}{section}

\newcommand{\warn}[1]{{\leavevmode\color{red}[#1]}}

\begin{document}


We are grateful to the referee for their careful reading and their comments and suggestions. We have implemented most of their requests. For the remaining few, our answers are below.

(15) $D$ was defined in the second paragraph of 2.5

(23) I don't understand the suggested correction, because it is the same as what is written now. Perhaps a copy-past mistake?

(24) This is the notation used in [Kal16b]. It is meant to suggest taking the preimage in $\hat{\bar H}$ or $\hat{\bar G}$ of a set of Galois-fixed points. For this we think of $S_\varphi$ as Galois-fixed points in $\hat G$ for the Galois action given by $\varphi$.

(32) The Lie group $N(\R)$ is a nilpotent group, a condition which is used in the cited theorem.

(38) I guess it's a matter of taste. I'm allowing an arbitrary fourth root of unity.

(44) $A$ contains elements outside of $\hat G$, while $B$ lies in $\hat G$, so $B$ never equals $A$.

\end{document}